IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-15 paper/abstract.tex
Refocus abstract

\begin{abstract}
Many important security problems in JavaScript, such as browser extension
security, untrusted JavaScript libraries and
safe integration of mutually distrustful websites (mash-ups), may be effectively addressed using an efficient implementation
of information flow control.
We formally define a system in which a coarse-grained dynamic IFC system
can be designed once and then applied to any programming language
for which external effects can be controlled.  We use
this formalism to implement two IFC systems for JavaScript, and show how
it applies to other languages such as C.
We describe how this methodology offers design principles for
the construction of information flow control systems in more
traiditional settings, as well as compositional proofs for optimized
concrete implementations of IFC systems, which can be shown to
have interference by relating them to their fully isolated variants.
\end{abstract}

>>>>

\begin{abstract}
Web sites could compromise users' privacy by accidentally incorporating
error-prone or malicious third-party JavaScript. Informa\-tion-flow control
(IFC) is a promising technique to securely incorporate untrusted JavaScript into
web sites and it allows the safe integration of mutually distrustful websites
(mash-ups). Unfortunately, existing IFC approaches demand non-trivial
modifications to the JavaScript engine or a full instrumentation of the
JavaScript semantics in order to track how information flows inside web
applications. Inspired by operating system research, we present an alternative
technique based on attaching a single IFC policy to a single browsing context,
and therefore abstracting away from the internals of JavaScript. Specifically,
we provide a coarse-grained IFC monitor which does not require any modifications
to either JavaScript semantics or its engine---the approach only exposes a small
API to the JavaScript code in order to interact with the monitor. To reason
about our design principles, we describe a formal framework which then we
instantiate to provide guarantees to out monitor implementation in Firefox.
\end{abstract}
